Draft

### 2022-06-21 ms.tex
in Sec.2 revised partially as M, next would be Sec. 3 by K first round

\vspace{2mm}
\subsection{Seeds}\label{sec:seed}
The QLFs at high redshifts are determined by the original BH seeding and subsequent growth. 
Firstly we describe our model regarding the formation of BH seeds in progenitor DM halos 
that end up in high-$z$ quasar host galaxies with halo masses of $\Mh>10^{11}~\Msun$.
This is motivated by the observed masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
probed by \blue{$\CII$ line width estimation} \citep{2019ApJ...872L..29S}.
Therefore, we sample base halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6. 
We then generate 10$^4$ merger trees with each base halo mass backward in time using the {\tt GALFORM} 
semi-analytic algorithm based on the extended Press-Schechter formalism 
\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}, and study the BH seeds formed therein.

@@

% Figure 1 shows the BH seeds formed in progenitors of $\Mh = 10^{11}, 10^{12}$
\vspace{2mm}
\subsection{BH growth \& mass Function}\label{sec:MF}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. We have constraints on simulations and observations of lower redshift counterparts.
With seeds planted, we grow the BHs with a semi-analytical accretion rate model 
and study the BH mass distribution at redshift 6. 
\blue{(references + discussion)}
The growth model is captured by a limited number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by: 
%%%%%%%
%    Eq. 1
%%%%%%%
\begin{equation}
  \label{eq:mdot}
  \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd},
\end{equation}
where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
$\lambda = L/L_\mathrm{Edd}$ is the Eddington ratio that represents the strength of the accretion power.
Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $ according to the thin accretion disk model 
\citep{1973A&A....24..337S}, which is also consistent with 
the Soltan's argument  \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
% The high mass BH should be strangulated by as it grows, 
We introduce the mass dependency 
$f(M) = 0.5 \left[1+\left(M/10^8~\Msun\right)^\delta\right] ^ {-1}$, 
to suppress the high mass BH growth with a positive $\delta$. 
\blue{(references)}
With decreasing $\delta$, 
the model is reduced to an exponential growth independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.

@@

\vspace{2mm}
\subsection{QLF after obscuration}\label{sec:LF}
Furthermore, we can generate QLFs that is directly probed by high-$z$ observations.
%  compared with observations and in return constrain our model.
For a BH accreting with bolometric luminosity $\Lbol=\lambda L_\mathrm{Edd}$, 
its absolute magnitude $\Muv$ in the rest-frame ultraviolet (UV) band is given by:
%%%%%%%
%    Eq. 6
%%%%%%%
\begin{equation}
  \label{eq:M1450}
  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right).
\end{equation}
Here we adopt the bolometric correction factor $\fbol=4.4$ for the monochromatic UV band \citep{2006ApJS..166..470R}.
Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
the quasar abundances with different luminosities. 
However, we note that a vital ingredient to construct the observed QLF, 
is the luminosity dependent obscuration fraction, 
which decreases the fraction of the detectable quasars toward the dimmer population 
\citep{2003ApJ...598..886U,2014ApJ...786..104U,2008A&A...490..905H,2014MNRAS.437.3550M}, 
thus differs the normalization and shape of the observed QLF from the intrinsic one.

@@

\vspace{2mm}
\subsection{MCMC fitting}\label{sec:fitting}
In this section, we describe the Markov Chain Monte Carlo (MCMC) fitting procedure we adopt to optimize the parameters described in \S~\ref{sec:MF}. 
%%%%%%%
%    Fig. 2
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{contour.pdf}
\caption{
Posterior distributions of all the model parameters with 3 different $\fseed$ values, 
including the marginalized one dimensional projection and the two dimensional distribution between every two parameters. 
All the parameters converge to a single peak, 
and specially the $\log\delta$ is confined above the artificial $-3$ barrier, 
which is sufficiently low and can be neglected in the model.
}
\label{fig:contour}
\end{figure*}
%
% 1. data: observational MF LF; describe quadratic error in Willott 2010
Firstly the BHMF data is adopted from \citet{2010AJ....140..546W} (hereafter W10),
where they reconstruct the BHMF with the QLF and ERDF
extracted from the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6. 
The BHMF spanning $10^7 < M <10^{10}~\Msun$ is best constrained around $10^9~\Msun$, 
and the error is pronounced toward the low mass and high mass end.
We take 10 mass bins spacing evenly in logscale and a quadratic form of the error, 
covering the same ranges as their bootstrap resamples (see Figure 8 of W10). 
On the observed QLF side, we adopt the binned data and error bars from \citet{2018ApJ...869..150M}, 
over a wide range of $-30 < \Muv <-22$ mag (see their Table 4 and Figure 13).

@@

%%%%%%%
%    Fig. 4
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{fits_LF.pdf}
\caption{
Fit of QLF at $z=$ 6, by the best-fit parameters and one sigma spread as described in \ref{fig:fitmf}. 
The blue data points with error bars label the complete QLF sample from the observation by \citet{2018ApJ...869..150M}.
}
\label{fig:fitlf}
\end{figure*}

% 3. posterior
% Then evaluating the likelihood of the dataset reproducing the observed BHMF and QLF at $z=$ 6, 
% the Markov chain of samples converges to the best-fit (maximum likelihood) parameters.
Following the prior distribution, parameters are sampled to generate the synthetic BHMF and QLF dataset, 
which is then conjointly compared with the observational data. 
The offset between the model and data is evaluated as 
%%%%%%%
%    Eq. 8
%%%%%%%
\begin{align}
  \chi^2 = \sum_i
  \frac{\left(\log{\Phi_\mathrm{mod,i}} - \log{\Phi_\mathrm{obs,i}}\right)^2}{(\log{\Phi_\mathrm{err,i}})^2},
\end{align}
where $\Phi_\mathrm{mod,i}$ and $\Phi_\mathrm{obs,i}$ 
represent the modeled and observational values of $\Phi_\mathrm{M}$ ($\Phi_\mathrm{\Muv}$) in the \textit{i-}th BHMF (QLF) bin, and 
$\Phi_\mathrm{err,i}$ is the corresponding error.
Note that the equal constraints from the BHMF and QLF are realized by extracting
comparable numbers of data bins from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
% the constraint is actually insensitive to the choice of bin numbers. 
The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
with the models best reproducing the $z=$ 6 BHMF and QLF.

>>>>

\vspace{2mm}
\subsection{Seeds}\label{sec:seed}
The QLFs at high redshifts are determined by the original BH seeding and subsequent growth. 
Firstly we describe our model regarding the formation of BH seeds in progenitor DM halos 
that end up in high-$z$ quasar host galaxies with halo masses of $\Mh>10^{11}~\Msun$.
This is motivated by the estimated masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
probed by the $\left[\mathrm{C} \text{ II }\right]$ 158 $\micron$ fine structure line width \citep{2019ApJ...872L..29S}.
\blue{references}
Therefore, we sample base halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6. 
We then generate 10$^4$ merger trees with each base halo mass backward in time using the {\tt GALFORM} 
semi-analytic algorithm based on the extended Press-Schechter formalism 
\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}, and study the BH seeds formed therein.

@@

% Figure 1 shows the BH seeds formed in progenitors of $\Mh = 10^{11}, 10^{12}$
\vspace{2mm}
\subsection{BH growth \& mass Function}\label{sec:MF}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. We have constraints on simulations and observations of lower redshift counterparts.
With seeds planted, we grow the BHs with a semi-analytical accretion rate model 
and study the BH mass distribution at redshift 6. 
\blue{(references + discussion)}
The growth model is captured by a limited number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by: 
%%%%%%%
%    Eq. 1
%%%%%%%
\begin{equation*}
  \label{eq:mdot_1}
  \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd} ,
\end{equation*}
\begin{equation}
  \label{eq:mdot}
  \Mdot = \lambda f\left(M\right) \Mdot_\mathrm{Edd} ,
\end{equation}
% where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
where $\lambda = L/L_\mathrm{Edd}$ is the Eddington ratio,
and $\Mdot_\mathrm{Edd} = L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with the radiative efficiency $\eta_0$.
Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
according to the thin accretion disk model \citep{1973A&A....24..337S}, 
which is also consistent with the Soltan's argument \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
Then $\tEdd =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.
% The high mass BH should be strangulated by as it grows, 
We introduce the mass dependency 
$f(M) = 0.5 \left[1+\left(M/10^8~\Msun\right)^\delta\right] ^ {-1}$, 
to suppress the high mass BH growth with a positive $\delta$. 
\blue{(references)}
With decreasing $\delta$, 
the model is reduced to an exponential growth independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.

@@

\vspace{2mm}
\subsection{QLF after obscuration}\label{sec:LF}
Furthermore, we can generate QLFs that is directly probed by high-$z$ observations.
%  compared with observations and in return constrain our model.
For a BH accreting with bolometric luminosity $\Lbol=\lambda L_\mathrm{Edd}$, 
its rest-frame ultraviolot (UV) absolute magnitude $\Muv$ 
at 1450 $\mathrm{\AA}$ is given by: 
%%%%%%%
%    Eq. 6
%%%%%%%
\begin{equation}
  \label{eq:M1450}
  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right).
\end{equation}
Here we adopt the bolometric correction factor $\fbol=4.4$ for the monochromatic UV band \citep{2006ApJS..166..470R}.
Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
the quasar abundances with different luminosities. 
However, we note that a vital ingredient to construct the observed QLF, 
is the luminosity dependent obscuration fraction, 
which decreases the fraction of the detectable quasars preferentially in the dimmer population 
\citep{2003ApJ...598..886U,2014ApJ...786..104U,2008A&A...490..905H,2014MNRAS.437.3550M}, 
thus differs the normalization and shape of the observed QLF from the intrinsic one.

@@

\vspace{2mm}
\subsection{MCMC fitting}\label{sec:fitting}
In this section, we describe the Markov Chain Monte Carlo (MCMC) fitting procedure we adopt to optimize the parameters described in \S~\ref{sec:MF}. 
%%%%%%%
%    Fig. 2
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{contour.pdf}
\caption{
Posterior distributions of all the model parameters with $\fseed=0.1$ and 0.01, 
including the marginalized one dimensional projection and the two dimensional distribution between every two parameters. 
All the parameters converge to a single peak, 
and specially the $\log\delta$ is confined above the artificial $-3$ barrier, 
which is sufficiently low and can be neglected in the model.
}
\label{fig:contour}
\end{figure*}
%
% 1. data: observational MF LF; describe quadratic error in Willott 2010
Firstly the BHMF data is adopted from \citet{2010AJ....140..546W} (hereafter W10),
where they reconstruct the BHMF with the QLF and ERDF
extracted from the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6. 
The BHMF spanning $10^7 < M <10^{10}~\Msun$ is best constrained around $10^9~\Msun$, 
and the error is pronounced toward the low mass and high mass end.
We take 10 mass bins spacing evenly in logscale and a quadratic form of the error, 
covering the same ranges as their bootstrap resamples (see Figure 8 of W10). 
On the observed QLF side, we adopt the binned data and error bars from \citet{2018ApJ...869..150M}, 
over a wide range of $-30 < \Muv <-22$ mag (see their Table 4 and Figure 13).

@@

%%%%%%%
%    Fig. 4
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{fits_LF.pdf}
\caption{
Fit of QLF at $z=$ 6, by the best-fit parameters and one sigma spread as described in \ref{fig:fitmf}. 
The blue data points with error bars label the QLF from the observation by \citet{2018ApJ...869..150M}.
}
\label{fig:fitlf}
\end{figure*}

% 3. posterior
% Then evaluating the likelihood of the dataset reproducing the observed BHMF and QLF at $z=$ 6, 
% the Markov chain of samples converges to the best-fit (maximum likelihood) parameters.
Following the prior distribution, parameters are sampled to generate the synthetic BHMF and QLF dataset, 
which is then conjointly compared with the observational data. 
The offset between the model and data is evaluated as 
%%%%%%%
%    Eq. 8
%%%%%%%
\begin{align}
  \chi^2 = \sum_i
  \frac{\left(\log{\Phi_\mathrm{mod,i}} - \log{\Phi_\mathrm{obs,i}}\right)^2}{(\log{\Phi_\mathrm{err,i}})^2},
\end{align}
where $\Phi_\mathrm{mod,i}$ and $\Phi_\mathrm{obs,i}$ 
represent the modeled and observational values of $\Phi_\mathrm{M}$ ($\Phi_\mathrm{\Muv}$) in the \textit{i-}th BHMF (QLF) bin, and 
$\Phi_\mathrm{err,i}$ is the corresponding error.
Note that the equal constraints from the BHMF and QLF are realized by extracting
comparable numbers of data points from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
% the constraint is actually insensitive to the choice of bin numbers. 
The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
with the models best reproducing the $z=$ 6 BHMF and QLF.
